---
title: "WEEK4 COURSE PROJECT PML"
author: "Rajat Sagar"
date: "16th October' 2020"
output:
  html_document: default
  word_document: default
---


```{r}
library(caret)
library(knitr)

library(data.table)
library(rpart.plot)
library(rpart)

library(gbm)
library(ggplot2)

library(corrplot)

```
Now we will take the data and do the cleaning and then exploring the data. 

```{r}
testUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
traUrl  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

data_test <- read.csv(url(testUrl))
data_tra <- read.csv(url(traUrl))


```
now proceeding for the cleaning the input of the data

```{r}
training_data <- data_tra[, colSums(is.na(data_tra)) == 0]
testing_data <- data_test[, colSums(is.na(data_test)) == 0]
```
now we will prepare the data for pred. in which we will consider seventy percentage of the data for the training set and rest of the thirty percentage of the data for the testing data set
and testing_data will be used furthuer again for the prediction of the 20 of the cases 

```{r}
training_data <- training_data[, -c(1:7)]
testing_data <- testing_data[, -c(1:7)]
dim(training_data)
```

```{r}
set.seed(1234)
datatraining <- createDataPartition(data_tra$classe, p = 0.7, list = FALSE)
training_data <- training_data[datatraining, ]
testing_data <- training_data[-datatraining, ]
dim(training_data)
dim(testing_data)
```
now we will be removing the variables that are non zero from the data gives
```{r}
noneZero <- nearZeroVar(training_data)
training_data <- training_data[, -noneZero]
testing_data <- testing_data[, -noneZero]
dim(training_data)
dim(testing_data)
```


```{r}
plot_cor <- cor(training_data[, -53])
corrplot(plot_cor, order = "FPC", method = "color", type = "upper", tl.cex = 0.8, tl.col = rgb(0, 0, 0))
```

now in this as we can see that the corr. predic. are the ones with the dark colour intersec.

now we will be proceeding for the model building and for this we will use 2 different types of algorithms , trees and random forests for the prediction part 

```{r}
set.seed(20000)
tredec <- rpart(classe ~ ., data=training_data, method = "class")
rpart.plot(tredec)
```

now we will be validate the model 
```{r}
modelpre <- predict(tredec, testing_data, type = "class")
ab <- confusionMatrix(modelpre, testing_data$classe)
ab
```

```{r}
plot(modelpre)
```

now for the last part we will apply two models one by one 
the first one will be general boosted model and then the second one will be gbm model for this 
```{r}
set.seed(10000)
ctr_gbm <- trainControl(method = "repeatedcv", number = 5, repeats = 1)
valid_gbm <- train(classe ~ .,data=training_data, method = "gbm", trControl = ctr_gbm, verbose = FALSE)
valid_gbm$finalModel
```



